---
title: "Sequence Data Assignment"
author: "Logan Wisteard (20104157)"
date: "16/02/2022"
output: pdf_document
---
#GitHub username: LoganWisteard
#link to GitHub repository:https://github.com/LoganWisteard/Rentrez

#Load dplyr
```{r}
library(dplyr)
```

#Set working directory
```{r}
setwd("/Users/loganwisteard/Desktop/homefolder/Rentrez")
```

#Import sequences.csv file 
```{r}
sequences <- read.csv("./sequences.csv")
```

#Print each sequence
```{r}
print(sequences$Sequence)
```

#Count the number of each base pair (A, T, C and G), in each of the three sequences.
```{r}
nucleotides <- sequences %>% 
  mutate(SequenceID = gsub(">(\\w+\\.\\d+).*", "\\1", sequences$Name),
         A = nchar(gsub("[CTG]", "", sequences$Sequence)),
         T = nchar(gsub("[ACG]", "", sequences$Sequence)),
         C = nchar(gsub("[ATG]", "", sequences$Sequence)),
         G = nchar(gsub("[ATC]", "", sequences$Sequence)))
```

#Print out the number of each nucleotide as a table for each of the three sequences.

```{r}
print(nucleotides[c("SequenceID", "A", "T", "C", "G")])
```

#Include an image of a bacteria from the internet, and a link to the Wikipedia page about Borrelia burgdorferi

[Image of B. burgdorferi](https://upload.wikimedia.org/wikipedia/commons/thumb/f/f3/Borrelia_burgdorferi_%28CDC-PHIL_-6631%29_lores.jpg/330px-Borrelia_burgdorferi_%28CDC-PHIL_-6631%29_lores.jpg)  

Wikipedia article on *Borrelia burgdorferi* (https://en.wikipedia.org/wiki/Borrelia_burgdorferi#:~:text=Borrelia%20burgdorferi%20is%20a%20bacterial,known%20to%20cause%20the%20disease) 


#Calculate GC Content (% of nucleotides that are G or C) 
```{r}
nucleotides %>% summarise(SequenceID = SequenceID, GC = (C + G)/nchar(Sequence))
```

#create a final table showing GC content for each sequence ID
```{r}
GC_tab <- matrix(c("HQ433692.1", "44.28%", "HQ433694.1", "44.07%", "HQ433691.1", "44.07%"),ncol=2,byrow=TRUE)
colnames(GC_tab) <- c("Sequence ID","GC Content")
GC_tab<- as.table(GC_tab)
print(GC_tab)
```



